An FMI-Based Initialization Plugin for INTO-CPS Maestro 2\thanks{We are grateful to the Poul Due Jensen Foundation, which has supported the establishment of a new Centre for Digital Twin Technology at Aarhus University. Finally, we thank the reviewers for the thorough feedback.}

### 2020-11-13 background.tex
Updated report to handin

A graph of the dependencies of a co-simulation scenario is established from the interconnected variables by \cref{def:initialization_graph}. The graph is the foundation for the calculation of the initialization procedure and is therefore referred to as the Initialization Graph. The graph construction is similar to the one in \cite{Gomes2019c}, except the later focuses on a general co-simulation step, while this work focus on the initialization phase.

@@

\subsection{INTO-CPS Maestro 2}
INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}.}~\cite{Thule2019b} is a framework for creating simulation specifications and executing such specifications. The framework is FMI-based and set to supersede Maestro~\cite{Maestro} with the main goal of supporting research into co-simulation based on FMI.

>>>>

A graph of the dependencies of a co-simulation scenario is established from the interconnected variables by \cref{def:initialization_graph}. The graph is the foundation for the calculation of the initialization procedure and is therefore referred to as the Initialization Graph. The graph construction is similar to the one in \cite{Gomes2020b}, except the later focuses on a general co-simulation step, while this work focus on the initialization phase.

@@

\subsection{INTO-CPS Maestro 2}
INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}.}~\cite{Thule2020a} is a framework for creating simulation specifications and executing such specifications. The framework is FMI-based and set to supersede Maestro~\cite{Maestro} with the main goal of supporting research into co-simulation based on FMI.

### 2020-11-13 conclusion.tex
Updated report to handin

\section{Concluding Remarks}\label{sc:summary}
This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario potentially containing algebraic loops.
The initialization procedure optimizes the initialization order by grouping variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
This approach supports the initialization of a co-simulation scenario containing algebraic loops by using fixed point iteration. 
%The approach discards all co-simulation scenarios, not adhering to the law of convergence defined in \cref{def:convergence}.
The approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobi \cite{Palensky2017}. 
The approach is realized as an expansion plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
Future work includes formal verification of the plugin using the Logika framework\cite{inbook}.
We will also look into the generation of a verification strategy for the whole Maestro 2 framework to examine how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.

>>>>

\section{Concluding Remarks}\label{sc:summary}
This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario potentially containing algebraic loops.
The initialization procedure optimizes the initialization order by grouping variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
This approach supports the initialization of a co-simulation scenario containing algebraic loops by using fixed point iteration. 
%The approach discards all co-simulation scenarios, not adhering to the law of convergence defined in \cref{def:convergence}.
The approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobi \cite{Palensky2017}. 
The approach is realized as an expansion plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
Future work includes formal verification of the plugin using the Logika framework\cite{Robby2018}.
We will also look into the generation of a verification strategy for the whole Maestro 2 framework to examine how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.

### 2020-11-13 introduction.tex
Updated report to handin

\section{Introduction}\label{sc:introduction}
Cyber-physical systems (CPS) are becoming ever more sophisticated, while market pressure shortens the available development time. One of the tools to manage the increasing complexity of such systems is co-simulation since it tackles their heterogeneous nature. Co-simulation is a technique to combine multiple black-box simulation units to compute the combined models' behavior as a discrete trace (see, e.g., \cite{Kubler2000, Gomes2018}). The simulation units, often developed independently from each other, are coupled using a master algorithm, often developed independently, that communicates with each simulation unit via its interface. This interface comprises functions for setting/getting inputs/outputs and computing the associated model behavior over a given time interval.
The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012, fmi_2019} is such an interface prescribing how to communicate with each simulation unit. The interface is used to connect different simulation units, called Functional Mock-up Units (FMUs), exchange values between them, and make them progress in time.

@@

Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a deterministic co-simulation result\cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation, Gomes2019c}. This choice is driven by the fact that not all co-simulation scenarios containing algebraic loops are valid since those algebraic loops never converge, or might converge to unexpected solutions. However, as shown in \cref{sec:case_study}, solving algebraic loops can be essential to obtaining valid simulation results, and a well-established co-simulation framework should be able to handle these scenarios.

\textit{Contribution:} This paper describes an approach for calculating the initialization order of an FMI-based co-simulation in linear time of the number of interconnected variables, even when algebraic loops are present.
% The approach complies with the semantics of FMI and supports the initialization of algebraic loops between interconnected FMU variables and identifies divergence in a co-simulation scenario. 
The approach does not put any constraints on the master algorithm chosen to carry out the simulation. 
The approach is realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2), introduced in \cite{Thule2020a}.
The realized plugin has been tested for various co-simulation scenarios and compared to an existing Initializer that has been validated through academic and industrial applications. 
Furthermore, the calculated initialization order is systematically verified by the semantics of co-simulation introduced in \cite{gomes_lucio_vangheluwe_2019,Gomes2019c}.

>>>>

\section{Introduction}\label{sc:introduction}
Cyber-physical systems (CPS) are becoming ever more sophisticated, while market pressure shortens the available development time. One of the tools to manage the increasing complexity of such systems is co-simulation since it tackles their heterogeneous nature. Co-simulation is a technique to combine multiple black-box simulation units to compute the combined models' behavior as a discrete trace (see, e.g., \cite{Kubler2000,Gomes2018}). The simulation units, often developed independently from each other, are coupled using a master algorithm, often developed independently, that communicates with each simulation unit via its interface. This interface comprises functions for setting/getting inputs/outputs and computing the associated model behavior over a given time interval.
The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012,FMI2014} is such an interface prescribing how to communicate with each simulation unit. The interface is used to connect different simulation units, called Functional Mock-up Units (FMUs), exchange values between them, and make them progress in time.

@@

Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a deterministic co-simulation result\cite{Amalio2016,Broman2013,Gomes2020b}. This choice is driven by the fact that not all co-simulation scenarios containing algebraic loops are valid since those algebraic loops never converge, or might converge to unexpected solutions. However, as shown in \cref{sec:case_study}, solving algebraic loops can be essential to obtaining valid simulation results, and a well-established co-simulation framework should be able to handle these scenarios.

\textit{Contribution:} This paper describes an approach for calculating the initialization order of an FMI-based co-simulation in linear time of the number of interconnected variables, even when algebraic loops are present.
% The approach complies with the semantics of FMI and supports the initialization of algebraic loops between interconnected FMU variables and identifies divergence in a co-simulation scenario. 
The approach does not put any constraints on the master algorithm chosen to carry out the simulation. 
The approach is realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2), introduced in \cite{Thule2020a}.
The realized plugin has been tested for various co-simulation scenarios and compared to an existing Initializer that has been validated through academic and industrial applications. 
Furthermore, the calculated initialization order is systematically verified by the semantics of co-simulation introduced in \cite{gomes_lucio_vangheluwe_2019,Gomes2020b}.

### 2020-11-13 relatedwork.tex
Updated report to handin

\section{Related Work}
Prior work \cite{Gomes2019, BromanCompositionCo-Simulation} is looking into the generation of co-simulation algorithms (both master and initialization algorithms) for FMI-based scenarios. Their generation technique is like ours, based on a dependency graph of the operations of a co-simulation step. Both Gomes and Broman present an approach for using the topological order of a dependency graph to establish a correct order of operations in a co-simulation step of a given co-simulation scenario.
The work by Gomes et al. \cite{Gomes2019} does also define the criteria for a correct co-simulation step. Their work has many similarities with ours. However, their work is mostly concerned with the theoretical aspect of co-simulation algorithm generation and verification, while our work has a more practical nature. Gomes et al. do also not consider the handling of algebraic loops, which is a key feature of our approach. Furthermore, the approach taken in our work is only concerned with the initialization procedure of a co-simulation.

Broman et al. \cite{BromanCompositionCo-Simulation} also suggest to use the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of port-operations. Nevertheless, they explicitly specify the requirement for cycle freedom in the dependency graph as a precondition for generating a valid co-simulation. It means they refuse all co-simulation scenarios containing algebraic loops. It is a significant difference to our approach that applies a fixed point iteration strategy to handle these scenarios. Also, the approach in this paper is more specialized because it only considers the initialization of a co-simulation, which means it deals with non-interconnected variables.

Amalio et al. \cite{Amalio2016CheckingCo-simulation} investigate how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS. The publication's purpose is like ours, to avoid invalid co-simulation scenarios. Nevertheless, they achieve this by excluding co-simulation scenarios containing algebraic loops. Their method is realized in a co-simulation tool, INTO-SysML\cite{Miyazawa2016INtegratedModelling}. Formal methods form the basis of their work (Theorem Proving and Model-checking). It will be an inspiration for the future work of formally verifying the plugin and other parts of Maestro 2.

>>>>

\section{Related Work}
Prior work \cite{Gomes2019,Broman2013} is looking into the generation of co-simulation algorithms (both master and initialization algorithms) for FMI-based scenarios. Their generation technique is like ours, based on a dependency graph of the operations of a co-simulation step. Both Gomes and Broman present an approach for using the topological order of a dependency graph to establish a correct order of operations in a co-simulation step of a given co-simulation scenario.
The work by Gomes et al. \cite{Gomes2019} does also define the criteria for a correct co-simulation step. Their work has many similarities with ours. However, their work is mostly concerned with the theoretical aspect of co-simulation algorithm generation and verification, while our work has a more practical nature. Gomes et al. do also not consider the handling of algebraic loops, which is a key feature of our approach. Furthermore, the approach taken in our work is only concerned with the initialization procedure of a co-simulation.

Broman et al. \cite{Broman2013} also suggest to use the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of port-operations. Nevertheless, they explicitly specify the requirement for cycle freedom in the dependency graph as a precondition for generating a valid co-simulation. It means they refuse all co-simulation scenarios containing algebraic loops. It is a significant difference to our approach that applies a fixed point iteration strategy to handle these scenarios. Also, the approach in this paper is more specialized because it only considers the initialization of a co-simulation, which means it deals with non-interconnected variables.

Amalio et al. \cite{Amalio2016} investigate how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS. The publication's purpose is like ours, to avoid invalid co-simulation scenarios. Nevertheless, they achieve this by excluding co-simulation scenarios containing algebraic loops. Their method is realized in a co-simulation tool, INTO-SysML\cite{Miyazawa2016}. Formal methods form the basis of their work (Theorem Proving and Model-checking). It will be an inspiration for the future work of formally verifying the plugin and other parts of Maestro 2.
